💬 Generating response...

```latex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{ragged2e}
\usepackage{titlesec}
\usepackage{tikz}
\usepackage{xcolor}

\hypersetup{colorlinks=true, urlcolor=blue}
\pagestyle{empty}

% Vertical space compression
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlist[itemize]{leftmargin=1.5em, itemsep=0pt, parsep=0pt, topsep=0pt, partopsep=0pt}

% Section formatting
\titleformat{\section}{\vspace{-4pt}\normalfont\large\bfseries\centering}{\relax}{0em}{}
\titlespacing*{\section}{0pt}{4pt}{2pt} % Adjust spacing for sections

\begin{document}

% Header: Name and Contact Info
\begin{center}
    {\Huge \textbf{DINESH KUMAR S}} \\
    \vspace{2pt}
    \small
    \href{mailto:svani4830@gmail.com}{svani4830@gmail.com} \textbar \ +91 9342372124 \textbar \ 
    \href{https://github.com/SDineshKumar}{GitHub: SDineshKumar} \textbar \ 
    \href{https://linkedin.com/in/s-dineshkumar}{LinkedIn: s-dineshkumar} \textbar \ 
    \href{https://leetcode.com/Dinesh_Kumar_S/}{LeetCode: Dinesh\_Kumar\_S}
\end{center}

% Objective Section
\section*{OBJECTIVE}
\tikz \draw[line width=0.5pt, gray] (0,0) -- (\linewidth,0);
\vspace{2pt}
\small
A motivated AI \& Data Science Engineering graduate with practical experience in Guidewire, Generative AI, LLMs, and AWS Cloud. Seeking an entry-level Software Engineer position to apply strong technical skills in software development, contribute to innovative projects, and grow within a dynamic, collaborative team.

% Experience Section
\section*{EXPERIENCE}
\tikz \draw[line width=0.5pt, gray] (0,0) -- (\linewidth,0);
\vspace{2pt}

\textbf{Capgemini} \hfill (Present) \\
\textit{Guidewire Policy Center Training Program}
\begin{itemize}
    \item \textbf{Configuration:} Developed foundational understanding of setting up product models, coverage options, and policy terms within Policy Center. Applied business rules and validations to control policy behavior.
    \item \textbf{Integration:} Gained experience utilizing web services (SOAP) for connecting Policy Center with external systems. Implemented messaging protocols for automated data exchange and configured batch processes for scheduled tasks. Explored plugin development for custom functionality extension.
\end{itemize}

\textbf{Capgemini Udemy} \hfill \\
\textit{Generative AI \& Cloud Learning}
\begin{itemize}
    \item Completed "Generative AI for Beginners" and "LLM Engineering: Master AI, Large Language Models \& Agents" courses, acquiring skills in AI, LLMs, prompt engineering, and agent development relevant to software applications.
\end{itemize}

% Education Section
\section*{EDUCATION}
\tikz \draw[line width=0.5pt, gray] (0,0) -- (\linewidth,0);
\vspace{2pt}

\textbf{PANIMALAR ENGINEERING COLLEGE INDIA, TN} \hfill Dec 2021 - Dec 2025 \\
\textit{BTech in Artificial Intelligence and Data Science} \hfill Grade: 8.56
\begin{itemize}
    \item Awarded Copyrights Certification for a software idea in the Artificial Intelligence domain.
    \item Solved 450+ problems on LeetCode, significantly enhancing problem-solving and algorithmic skills crucial for software development.
    \item Achieved Global Rank 164 in IEEE Extreme 17.0 Coding Competition, earning an IEEE Excellence Award for programming prowess.
    \item Generated over 100+ monthly downloads on Hugging Face for developed applications, demonstrating project impact and technical proficiency.
\end{itemize}

\textbf{VAILANKANNI MATRIC HIGHER SECONDARY SCHOOL INDIA, TN} \hfill 2020-2021 \\
\textit{HSC Major in Mathematics and Biology} \hfill Attained 93\%

\textbf{VAILANKANNI MATRIC HIGHER SECONDARY SCHOOL INDIA, TN} \hfill 2018-2019 \\
\textit{SSLC, Major in Mathematics and Biology} \hfill Attained 93.3\%

% Technical Skills Section
\section*{TECHNICAL SKILLS}
\tikz \draw[line width=0.5pt, gray] (0,0) -- (\linewidth,0);
\vspace{2pt}
\small
\textbf{Programming Languages:} Python, Java, Gosu, SQL \\
\textbf{Frameworks/Platforms:} Guidewire Policy Center, AWS \\
\textbf{AI/ML/Cloud Technologies:} LLMs, Generative AI, RAG \\
\textbf{Tools \& Version Control:} Git, GitHub

% Publications Section
\section*{PUBLICATIONS}
\tikz \draw[line width=0.5pt, gray] (0,0) -- (\linewidth,0);
\vspace{2pt}
\small
\textbf{GCITC Conference IEEE Explore (2024)} - 'AI Weigh Live Tracking of Fruits and Vegetables'

% Languages Section
\section*{LANGUAGES}
\tikz \draw[line width=0.5pt, gray] (0,0) -- (\linewidth,0);
\vspace{2pt}
\small
Tamil, English, Telugu

% Extra-Curricular Activities Section
\section*{EXTRA-CURRICULAR ACTIVITIES}
\tikz \draw[line width=0.5pt, gray] (0,0) -- (\linewidth,0);
\vspace{2pt}
\small
\textbf{Sports:} Cricket, Chess, Carrom \textbar \ \textbf{Hobbies:} Art, Building useful applications.

\end{document}
```